Reflections on reflection for \\ intuitionistic set theories

### 2019-01-10 paper-reflection.tex
Effortlessly fix non-critical error

For addendum~(1), we redeclare~$S \defeq \bigcup_{k \in \NN} S_k^t$,
where~$S_k^t$ is the transitive closure of~$S_k$.

To ensure both addendum~(1) and addendum~(2), we redeclare~$S \defeq \bigcup_{k
\in \NN} P^\omega(S_k^t)$, where~$P^\omega(X) \defeq \bigcup_{\ell \in \NN}
P^{(\ell)}(X)$ is the union of iterated powersets.

For addendum~(3), we change the definition of~$S_{k+1}$ to include one summand
for each formula~$\varphi_i$.
\end{proof}

>>>>

For addendum~(1), we change the definition of~$S_{k+1}$ to be the transitive
closure of what is was before. To further accommodate addendum~(2), we change
this definition again, to be~$P^\omega$ of what is was before,
where~$P^\omega(X) \defeq \bigcup_{\ell \in \NN} P^{(\ell)}(X)$ is the union of
iterated powersets. For addendum~(3), we change the definition of~$S_{k+1}$ to
include one summand for each formula~$\varphi_i$.
\end{proof}
